---
title: " PubH 7462 Hw1 problem2"
author: "You Shan Shen"
date: "2022/2/1"
output: html_document
---
```{r Setup, echo=true, warning = FALSE, include=FALSE }
knitr::opts_knit$set(echo = TRUE,
root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)

theme_set(theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom"))
```

```{r, echo=TRUE, warning=FALSE}
library(tidyverse)

penguin.df <- read_rds("./data/penguin.RDS")

library(dplyr)

number_row <- nrow(penguin.df)

number_col <- ncol(penguin.df)

number_species <- penguin.df  %>% count(species)

number_island <- penguin.df  %>% count(island)

bill_length_mm <- penguin.df  %>% select(bill_length_mm)

bill_depth_mm <- penguin.df  %>% select(bill_depth_mm)

flipper_length_mm <- penguin.df  %>% select(flipper_length_mm)

body_mass_g <- penguin.df  %>% select(body_mass_g)

number_sex <- penguin.df  %>% count(sex)

number_year <- penguin.df  %>% count(year)

mu_fliper <- mean( penguin.df$flipper_length_mm, na.rm = TRUE ) %>% 
             round( digits = 3)

sd_fliper <- sd(penguin.df$flipper_length_mm, na.rm = TRUE) %>% 
            round( digits = 3)

mu_bill <- mean( penguin.df$bill_length_mm, na.rm = TRUE ) %>% 
           round( digits = 3)

sd_bill <- sd(penguin.df$bill_length_mm, na.rm = TRUE) %>%  
           round( digits = 3)

#mu_bill <- penguin.df  %>% mean( bill_length_mm, na.rm = TRUE )

```

Penguins data set has ` r number_row ` observations and ` r number_col ` variables.
Species is a factor denoting penguin species (Adélie, Chinstrap and Gentoo) and the number of each group is ` r number_species `.
Island is a factor denoting island in Palmer Archipelago, Antarctica (Biscoe, Dream or Torgersen) and the number of each island is ` r number_island `.
` r bill_length_mm ` is a number denoting bill length (millimeters).
` r bill_depth_mm ` is a number denoting bill depth (millimeters).
` r flipper_length_mm ` is an integer denoting flipper length (millimeters).
` r body_mass_g ` is an integer denoting body mass (grams)
Sex is a factor denoting penguin sex (female, male). The number for each sex and for missing data is ` r number_sex `.
Year is an integer denoting the study year (2007, 2008, or 2009) and the number for each year is ` r number_year `. 
The mean and standard deviation of flipper is ` r mu_fliper` and ` r sd_fliper ` respectively.
The mean and standard deviation of bill length is ` r mu_bill ` and ` r sd_bill ` respectively.

```{r, echo=TRUE, warning=FALSE}
library(ggplot2)
penguin.df %>%
drop_na %>%
ggplot(aes(x = bill_length_mm , y = flipper_length_mm)) +
geom_point(aes(color=species)) +
facet_wrap(~sex, scales= "free" ) +
ggtitle( "palmerpenguins" ) +
xlab( "Bill Length (mm)" ) + 
ylab( "Fliper length (mm)" )

```

